---
title: "R Notebook"
output: 
  html_notebook: 
    toc: yes
---

## Questions:

### 1. What are the first 3 values that result?


Load Data
```{r}

download.file("https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Fss06hid.csv

",destfile="housing.csv")

housing<-read.csv("housing.csv")
str(housing)

```


Load Package
```{r}
library(dplyr)
```


```{r}
housing$agricultureLogical<-as.logical(housing$ACR==3&housing$AGS==6)
which(agricultureLogical)

```


### 2.Use the parameter native=TRUE. What are the 30th and 80th quantiles of the resulting data? (some Linux systems may produce an answer 638 different for the 30th quantile)



```{r}
download.file("https://d396qusza40orc.cloudfront.net/getdata%2Fjeff.jpg",destfile = "professor.jpeg",mode = "wb")

library(jpeg)
professor<-jpeg::readJPEG("professor.jpeg",native = TRUE)
quantile(professor,c(0.3,0.8))

```


### 3. Match the data based on the country shortcode. How many of the IDs match? Sort the data frame in descending order by GDP rank (so United States is last). What is the 13th country in the resulting data frame?


```{r}
library(data.table)
```

```{r}
download.file("https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FGDP.csv",destfile = "GDP.csv",method = 'curl')
GDP_dt<-fread("GDP.csv",skip = 5,nrows = 190,select = c(1,2,4,5),col.names = c("CountryCode", "Rank", "Economy", "Total"))
summary(GDP_dt)

download.file("https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FEDSTATS_Country.csv",destfile = "education.csv",method = 'curl')

education<-fread("education.csv")
```


```{r}
education%>%
  inner_join(GDP_dt)%>%
  arrange(desc(Rank))%>%
  head(n=13)
  

```

### 4. What is the average GDP ranking for the "High income: OECD" and "High income: nonOECD" group?

```{r}
education%>%
  inner_join(GDP_dt)%>%
  group_by(`Income Group`)%>%
  summarise(avg_rank=mean(Rank))
```

### 5.Cut the GDP ranking into 5 separate quantile groups. Make a table versus Income.Group. How many countries are Lower middle income but among the 38 nations with highest GDP?

```{r}
library(Hmisc)
```


```{r}
combined<-education%>%
  inner_join(GDP)%>%
  mutate(GDP_ranking=cut2(Rank,g=5))
  
  table(combined$GDP_ranking,combined$`Income Group`)
```


